---
title: "PA1"
output: html_document
---

## Markdown file

Code for reading in the dataset and/or processing the data
```{r}
  library("dplyr")
  setwd("/Users/Ziwei/Desktop/Rworkspace")
  f <- read.csv("activity.csv")
```
Histogram of the total number of steps taken each day
```{r}
  tot <- aggregate(steps ~ date, data = f, FUN = sum)
  hist(tot$steps, main = "Histogram of total number of steps", xlab = "steps")
```

Mean and median number of steps taken each day
```{r}
  mean(tot$steps)
  median(tot$steps)
```
Time series plot of the average number of steps taken
```{r}
  int_avg <- aggregate(steps ~ interval, data = f, FUN = mean, na.rm = TRUE)
  plot(int_avg$interval,int_avg$steps, type = "l", ylab = "steps", xlab = "interval", main = "Time series plot of the average number of steps ")
```

The 5-minute interval that, on average, contains the maximum number of steps
```{r}
  m <- max(int_avg$steps)
  int_avg$interval[int_avg$steps == m]
```
Code to describe and show a strategy for imputing missing data

There are
```{r}
  sum(is.na(f$steps))
```
mssing data

I use the mean for that 5-minute interval to imput the missing values
```{r}
  temp <- f[is.na(f$steps),]$interval
  f[is.na(f$steps),]$steps <- int_avg$steps[match(f$interval[is.na(f$steps)], int_avg$interval)]
```
Histogram of the total number of steps taken each day after missing values are imputed
```{r}
  tot <- aggregate(steps ~ date, data = f, FUN = sum)
  hist(tot$steps, main = "Histogram of total number of steps", xlab = "steps")
```
mean and median for new data set:
```{r}
  mean(tot$steps)
  median(tot$steps)
```
We can see the mean and median do change after imputing missing values


Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r}
  f <- mutate(f,WD = weekdays(as.Date(f$date)))
  f$WD = ifelse(f$WD %in% c("Saturday", "Sunday"), "weekend", "weekday")

  par(mfcol = c(2,1))
  int_avg <- aggregate(steps ~ interval, data = subset(f,WD == "weekday"), FUN = mean, na.rm = TRUE)
  plot(int_avg$interval,int_avg$steps, type = "l", ylab = "steps", xlab = "interval", main = "Weekday average number of steps ")

  int_avg <- aggregate(steps ~ interval, data = subset(f,WD == "weekend"), FUN = mean, na.rm = TRUE)
  plot(int_avg$interval,int_avg$steps, type = "l", ylab = "steps", xlab = "interval", main = "Weekend average number of steps ")
  
```
We can see the average of steps of weekdays and weekends are a little bit different.